### 2023-06-01 letter-one/letter-one.tex
On Gurudom

\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}

@@

Enclosed is a copy of Charlotte Joko Beck's ``Nothing Special''.
I do not endorse her teaching or her particular brand of Buddhism (nor any other) but, immediately following my second 10-day meditation course, I found her writing to be a great help in untangling the confusion which surfaced from my experience.
Perhaps you will also find it similarly useful.

@@

>>>>

\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}
\newcommand\hr{\par\vspace{-.5\ht\strutbox}\noindent\hrulefill\par}

@@

Enclosed is a copy of Charlotte Joko Beck's ``Nothing Special''.
I do not endorse her teaching or her particular brand of Buddhism (nor any other) but, immediately following my second 10-day meditation course, I found her writing to be a great help in untangling the confusion which surfaced from my experience.
Perhaps you will also find it similarly useful.
It has little or nothing to do with the following letter.

@@

It's impossible for me to write something for every economy, cultural context, linguistic background, and ambient religion.
Instead, I'll try my best to relate my personal experiences in a way that might be appreciated globally -- as a story, if nothing else.

\hr

There were no gurus in my childhood.
By the time I was old enough to appreciate what religion and spirituality meant to the adults in my community,
